---
title: "Análisis exploratorio de datos de viviendas"
author: "Danna De la Hoz y Mary Silva"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
description: "Análisis exploratorio del conjunto de datos de viviendas."
---

# Presentación {-}

## Análisis exploratorio de datos de viviendas

**Métodos Estadísticos**

**Integrantes:**  
Danna Valentina De la Hoz Orduz y
Mary Isabella Silva Barbosa

**Universidad del Norte**

**2026**

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
